test

### 2024-02-07 test.qmd
Update test.qmd

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
3
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

>>>>

#data cleaning -> a column called year will be produced in the data 
#(you can change the names of the data set)
data_strikes_year <- dataset_strikes
data_strikes_year$Year <- substr(data_strikes_year$date, 1, 4)
